Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-04-24 development.tex
ah, second thoughts!

While peer review is able to catch many bugs and problems with source
code changes, \enzo\ is also subject to ``answer'' testing.  We have
created a set of parameter files and problem types that exercise the
underlying machinery of \enzo.  These ``test problems'' have
affiliated ``tests,'' which consist of scripts that use \texttt{yt}
\citep{2011ApJS..192....9T} to produce results such as mass
distribution, projections, profiles and so on.  The testing
infrastructure then evaluates whether the variation in the new results
compared to a ``gold standard'' of results has exceeded an acceptable
threshold, typically set to roughly single precision.  Optionally, for
those test problems that are deemed unsafe to change to any precision,
the tests also produce hashes of the outputs; these hashes will only
remain unchanged in the event of bitwise identicality between results.
The results of the gold standard are versioned and stored in Amazon
S3, enabling remote testing to proceed.  While the testing process --
building, running, analyzing and comparing -- is not yet automated
against incoming pull requests, we hope to deploy that functionality
in the future.  The primary challenge is that of compute time; the
tests are organized into multiple categories, including by the
expected run time, but the full suite of tests can take several days
to run on multiple processors.

>>>>

While peer review is able to catch many bugs and problems with source
code changes, \enzo\ is also subject to ``answer'' testing.  We have
created a set of parameter files and problem types that exercise the
underlying machinery of \enzo.  These ``test problems'' have
affiliated ``tests,'' which consist of scripts that use \texttt{yt}
\citep{2011ApJS..192....9T} to produce results such as mass
distribution, projections, profiles and so on.  The testing
infrastructure then evaluates whether the variation in the new results
compared to a ``gold standard'' of results has exceeded an acceptable
threshold, typically set to roughly single precision.  Optionally, for
those test problems that are deemed unsafe to change to any precision,
the tests also produce hashes of the outputs; these hashes will only
remain unchanged in the event of bitwise identicality between results.
The results of the gold standard are versioned and stored in Amazon
S3, enabling remote testing to proceed.  While the testing process --
building, running, analyzing and comparing -- is not yet automated
against incoming pull requests, we hope to deploy that functionality
in the future.  The primary challenge is that of compute time; the
tests are organized into multiple categories, including by the
expected run time, but the full suite of tests can take several days
to run.
